rgbif: R client for working with GBIF species occurrence data

### 2015-11-25 manuscript.tex
pdf updated

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  pt 1
\item
  pt 2
\item
  The \texttt{rgbif} package has already been used in 22 scholarly
  publications (as of 2015-11-14).
\item
  pt 4
\end{itemize}

>>>>

The \texttt{rgbif} R package provides a programmatic interface to GBIF's
application programming interface (API) - a powerful tool for making
research using species occurrence data reproducible. In fact, the
\texttt{rgbif} package has already been used in 22 scholarly
publications (as of 2015-11-14).

The \texttt{rgbif} package is relatively stable now, and should not have
many breaking changes unless necessitated due to changes in the GBIF
API.

One area of focus in the future is to attempt to solve many use cases
that have been brought up with respect to GBIF data. For example, some
specimens are included in GBIF that are located in botanical gardens.
For many research questions, researchers are interested in ``wild'' type
occurrences, not those in human curated scenarios. Making removal of
these occurrences easy would be very useful, but is actually quite a
hard problem.
